\documentclass{my_cv}

\usepackage[skins]{tcolorbox}
\usepackage{ragged2e}
\begin{document}

\begin{minipage}[t]{0.52\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Yash Singh}}}}} % First name
	
	%\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Singh}}}}} % Last name
	
	\vspace{2pt}
	
	{\huge Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.29\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{8}{Blacksburg, VA, USA}\\
	\icon{Phone}{8}{(540)-317-0341}\\
	\icon{At}{8}{\href{mailto:yash1o1@outlook.com}{yash1o1@outlook.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.50\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{8}{\href{https://yash-1o1/github.io/}{yash-1o1/github.io}}\\
    \icon{Linkedin}{8}{\href{https://linkedin.com/in/yash1o1}{Yash Singh}}\\
	\icon{Github}{8}{\href{https://github.com/yash-1o1}{yash-1o1}}\\
\end{minipage}

\vspace{2pt}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.47\textwidth} % 40% of the page width for the introduction text
	%\cvsect{Who Am I?}
	\vspace{0.5cm}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

\section{\faGraduationCap}{WHO AM I?}
{A detailed-oriented, responsible individual with a get-it-done on time and high quality product spirit. I also happen to be a good learner and a team player/leader who likes to put his analytical, problem solving and communication skills to get the task done with mind set to start contributing from day one. \textbf{\emph{\href{https://yash-1o1.github.io/}{Visit my website to know more about me!}}}}

\vspace{0.4cm}

\section{\faGraduationCap}{EDUCATION}
\work{Virginia Tech - 2021}
{}{Bachelors of Engineering - Computer Engineering}{}
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.47\textwidth} % 50% of the page for the skills bar chart
	%\vspace{-\baselineskip} % Required for vertically aligning minipages
	\vspace{.1cm}
	\section{\faGraduationCap}{CORE SKILLS}
	\begin{barchart}{5.5}
		\baritem{Java}{45}
		\baritem{C,C++}{80}
		\baritem{Python}{90}
		\baritem{Git}{90}
		\baritem{MATLAB}{80}
		\baritem{SQL(MYSQL/NOSQL)}{45}
		\baritem{Photoshop/Illustrator}{90}
	\end{barchart}
\end{minipage} 

\vspace{.05cm}
\begin{multicols}{2}
\section{\faPencil}{SELECTED PROJECTS}
\work{Automated Warehouse Robot \newline Aug 2021 - Oct 2021}
    {Skills used: Python, SolidWorks, CSS, GitHub}%
    {
        • Led a team of 4 members to develop a warehouse robot that would automate the process of moving boxes. \newline
        • Managed the overall functioning and integration of code. \newline
        • Developed the algorithm for intercommunication of various different components over a MQTT server. \newline
        • Worked on the developed of the 3+ DOF robotic arm.
}
    {}

\work{Fire Hazard Detection System \newline May 2021 - Aug 2021}
    {Skills used: Python, Arduino, MIT App Inventor, GitHub}%
    {
       • Team lead with a team of 3 people where we developed a wireless sensor that could be deployed remotely. \newline
       • The team implemented a DC/DC converter to power the wireless sensor node via solar energy.\newline
       • Individually developed of the mobile GUI for the sensor, which was used to display the analog temperature readings taken by the sensor as digital readings. \newline
       • Contributed towards testing and debugging process.
}
    {}
    
\work{Graphic Mobile Banking Application \newline Aug 2020 - Dec 2020}
    {Skills used: C++, Qt, Git, Vagrant}%
    {   
         • A full stack app development which demonstrates my ability to work with back-end and the front-end. \newline
         • Used Qt cross platform for front-end development, made a GUI for a fully functional ATM.
         \newline
         • Worked with multi thread application so two processes were handled simultaneously for the back-end structure. \newline
         • Included various features like Open and Close Account, Withdraw, Deposit with pin protection. \newline
         • Incorporated a very wide range of error checking and thorough testing for TUI as well as the GUI.
    }
    {}
    
\vspace{-1.5cm}

\section{\faPencil}{SELECTED EXPERIENCES}
\vspace{-0.2cm}
\work{Tata Consultancy Services \newline Jun 2020 - Sep 2020}
    {Software Engineering Intern}%
    {
        • Did 2 case studies which had to be presented to the clients. \newline
        • Performed initial client analysis and assessment to begin research process. \newline
        • Worked on approach towards the development of new block-chain technologies and completed market research. \newline
        • Managed to get a new client for the company.
}
    {}

\work{CDAC \newline Dec 2019 - Jan 2020}
    {Software Development Intern}
    { 
        • Was Part of the SQL team to perform testing for different applications where I assisted with network design and optimization & ran tests to ensure they work properly. \newline
        • Got Trained and worked with SQL and NoSQL. \newline
        • Used these database for development of reports, using advanced queries to achieve reporting requirements. \newline
        • Reduced the manual entry of queries by 40\%, by creating documentation addressing common technical issues.
}
    {}
    
\work{Follett \\ Sep 2018 - Nov 2019}%
    {Hardware Technician and Sales Service Representative}%
    {
}
    {}

\vspace{-0.6cm}
    
\work{BlackStone \\ Jun 2018 - Aug 2018}%
    {Software Intern}%
    {
        • The summer training was successfully completed with the company's Knowledge Services Division. \newline
        • Here I received basic training in R and Python. \newline
        • Then was given the role write test cases for the beta releases for debugging the existing issues. \newline
        • Supported previous model releases by analyzing and suggesting code fixes for minor existing software problems.
    }
    {}
%\section{\faStar}{CERTIFICATIONS}
%\work{Artificial Intelligence and Machine Learning using Python May-July 2019}%
%    {NSUT}%
%    {Course based on AI and Machine Learning which covered NumPy, Pandas, Logistics Regression, Artificial Neural Networks, Deep Learning Frameworks and TensorFlow.}
%    {}
    
%\work{Adobe Photoshop / Graphic designing July 2017}%
%    {}%
%    {Three months course from MAAC, a high-end 3D animation and VFX brand of Aptech.}
%    {}
\end{multicols}
\end{document}